Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-10-31 1.Paper/Paper.Rmd
Update Paper.Rmd

Overall, both Heckman-based imputation (1l. and 2l.) models provide less biased estimates of the coefficient parameters in MNAR scenarios, but the random effects estimates on the 1l.Heckman are far away from the true values as no cluster information was considered at all.
Regarding the coverage, the Heckman-IPD imputation method provides the best coverage values across all the $\rho$ scenarios with a coverage level close to the nominal 95\% interval. Even 2l.Heckman is not properly a randomization-valid (Rubin 1987b) method across all the $\rho$ values it leads to better results in terms of bias and coverage compared to the evaluated methods.

The precision of the Heckman IPD separated seems it is better than the Heckman IPD full version, specially in the MAR scenarios, when we checked simulation results it seems that the high variability on the full version is related to simulations in which singularity fit that it is an indication that the model is over-fitted.

@@

One of the major limitations of our method is that it needs a valid restriction variable, which in some contexts is difficult to establish at the individual study level and can be even more challenging if one tries to find a valid exclusion variable across clusters.
Also the method is sensitive to the value of the correlation between the selection equation and outcome (rho), and in general it is observed that it can lead to biased results on fixed global parameters i.e. without variation across clusters.Similarly, the method can be sensitive to both the sample size and the number of studies included in the database. On the one hand a small sample size at the individual study level can affect not only the precision of estimates but also the convergence of the method since it requires a minimum sample size to estimate all the parameters of the Heckman model which can be at least twice the number of parameters required in a MAR prediction model. On the other hand, a high number of studies that may improve the precision of the estimators may also make the estimation of the marginal parameters more difficult and also considerably increase the processing time of our method.

>>>>

Overall, both Heckman-based imputation (1l. and 2l.) models provide less biased estimates of the coefficient parameters in MNAR scenarios, but the random effects estimates on the 1l.Heckman are far away from the true values as no cluster information was considered at all.
Regarding the coverage, the 2l.Heckman imputation method provides the best coverage values across all the $\rho$ scenarios with a coverage level close to the nominal 95\% interval. Even 2l.Heckman is not properly a randomization-valid (Rubin 1987b) method across all the $\rho$ values it leads to better results in terms of bias and coverage compared to the evaluated methods.

@@

One of the major limitations of our method is that it needs a valid restriction variable, which in some contexts is difficult to establish at the individual study level and can be even more challenging if one tries to find a valid exclusion variable across clusters.

Also the method is sensitive to the value of the correlation between the selection equation and outcome (rho), and in general it is observed that it can lead to biased results on fixed global parameters i.e. without variation across clusters.Similarly, the method can be sensitive to both the sample size and the number of studies included in the database. On the one hand a small sample size at the individual study level can affect not only the precision of estimates but also the convergence of the method since it requires a minimum sample size to estimate all the parameters of the Heckman model which can be at least twice the number of parameters required in a MAR prediction model. On the other hand, a high number of studies that may improve the precision of the estimators may also make the estimation of the marginal parameters more difficult and also considerably increase the processing time of our method.
